\textsf{Cyp2SQL -- Documentation}

### 2017-08-24 docs/latex/draftB.tex
Some bug fixes to ORDER BY and GROUP BY parts. Schema conversion tested against additional graph databases.
Licensing added.

\subsection{Known issues}
\begin{itemize}
\item The use of \texttt{WITH} is still quite constrained in its use
\item When predicates in the \texttt{WHERE} clause are added, they may sometimes lead to incorrect translations (mostly in the \texttt{WITH} parts of a multiple relationship Cypher input). It can be solved in some cases by adding the predicates in a different way in the original input (see example below)
\end{itemize}

@@

\subsection{List of test queries from OPUS}
\begin{verbatim}
MATCH p=shortestPath((f {name:"omega"})-[*1..6]->(t:Meta)) RETURN count(t);

>>>>

\section{Known issues}
\begin{itemize}
\item The use of \texttt{WITH} is still quite constrained in its use
\item Alias names cannot be the same as field names -- for example, \texttt{a.points AS points} would not work; \texttt{a.points AS points\_x} is fine however
\item Some labels from Neo4j may map to reserved keywords in SQL (such as \emph{Group} and \emph{User}) - in these cases the optimised table for these labels cannot be created
\item When predicates in the \texttt{WHERE} clause are added, they may sometimes lead to incorrect translations (mostly in the \texttt{WITH} parts of a multiple relationship Cypher input). It can be solved in some cases by adding the predicates in a different way in the original input (see example below)
\end{itemize}

@@

\section{List of test queries from OPUS}
\begin{verbatim}
MATCH p=shortestPath((f {name:"omega"})-[*1..6]->(t:Meta)) RETURN count(t);
